### 2021-05-11 analysis/statistical_analyses.Rmd
first commit
update analysis script

```{r libraries}
library(tidyverse)
library(here)
library(ggthemes)
library(lme4)
library(brms)
library(xtable)
```

```{r data, include=TRUE}
dpath_exp1 <- here("data", "responsesOnly_E1_100def.csv")
dpath_exp2 <- here("data", "responsesOnly_E2_100def.csv")

@@

@@

# use sum coding 
#options(contrasts=c("contr.sum", "contr.poly"))
options(contrasts=c("contr.treatment", "contr.poly"))

m0 <- glmer(ri ~ state_or_event + length + (1|participantnum), data = d1_stats1, 
            family = binomial(link = "logit"))

nchain <- 1 # for testing
niter <- 500 # for testing

nchain <- 8 # for real run
niter <- 4000 # for real run

@@

# use sum coding 
#options(contrasts=c("contr.sum", "contr.poly"))
options(contrasts=c("contr.treatment", "contr.poly"))

@@

nchain <- 1 # for testing
niter <- 500 # for testing

nchain <- 4 # for real run
niter <- 2000 # for real run

>>>>

```{r libraries}
library(tidyverse)
library(here)
library(ggthemes)
library(brms)
library(xtable)
```

```{r data, include=TRUE}
dpath_exp1 <- here("data", "E1_responses.csv")
dpath_exp2 <- here("data", "E2_responses.csv")

@@

# For simplicity run analyses on dual networks only

@@

options(contrasts=c("contr.treatment", "contr.poly"))

nchain <- 8 
niter <- 4000

@@

options(contrasts=c("contr.treatment", "contr.poly"))

@@

nchain <- 8 
niter <- 4000
